Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Checkpoint polishing and new try at dfiagram

\lstset{ language=Caml, basicstyle=\linespread{0.8}\upshape\sffamily,
keywordstyle=\upshape\sffamily\color{dkblue}, keepspaces=true,
framexleftmargin=1ex, framexrightmargin=1ex, showstringspaces=false,
commentstyle=\itshape\rmfamily,
emph={synth,project,perm,squash,normalize,using,ins,del,lens},
emphstyle=\upshape\sffamily\color{dkblue}, columns=flexible,
% BCP: I find this distracting:
% stringstyle=\sffamily\color{dkred},
mathescape, }

@@

The QRE lens combinators are inspired by the Boomerang lens combinators of the
same name. The $\kw{lift}(\ell)$ quotient lens enables a bijective lens
$\ell$ to be considered a quotient lens, with the equivalence relation applied
to both the source and target formats being the equality relation. The
regular combinators of concatenation `$\cdot$', Kleene star `$*$' and
`$|$' on QRE lenses exhibit the expected behaviour, with the caveat that these
combinators are strongly unambiguous. The composition operator `$;$' also
exhibits the expected behaviour, though the conditions that must be checked in
order for the composition to be well defined are perhaps unintuitive. The
reasons why these conditions are necessary will become more apparent when
proving normal forms for QRE lenses.

@@

For example, recall that in the \bibtex{} to EndNote transformation, we had the
QREs \cd{bibtex} and \cd{endnote} describing the \bibtex{} and EndNote records
respectively, and the bijective lens \cd{bib_to_end} that maps between
\cd{bibtex} and \cd{endnote}. The quotient lens that maps between
\cd{bibtex} and \cd{endnote} is given by the QRE lens

>>>>

\lstset{ language=Caml, basicstyle=\linespread{0.8}\upshape\sffamily,
keywordstyle=\upshape\sffamily\color{dkblue}, keepspaces=true,
framexleftmargin=1ex, framexrightmargin=1ex, showstringspaces=false,
keepspaces=true,
commentstyle=\itshape\rmfamily,
emph={synth,project,perm,squash,normalize,using,ins,del,lens},
emphstyle=\upshape\sffamily\color{dkblue}, columns=flexible,
% BCP: I find this distracting:
% stringstyle=\sffamily\color{dkred},
mathescape, }

@@

The QRE lens combinators are inspired by the Boomerang lens combinators of the
same name. The $\kw{lift}(\ell)$ quotient lens enables a bijective lens
$\ell$ to be considered a quotient lens, with the equivalence relation applied
to both the source and target formats being the equality relation. The
regular combinators of concatenation `$\cdot$', Kleene star `$*$' and
`$|$' on QRE lenses exhibit the expected behaviour\bcp{Is the behavior really
  ``expected''---i.e., will it be obvious to all readers?}, with the caveat
that these 
combinators are strongly unambiguous. The composition operator `$;$' also
exhibits the expected behaviour, though the conditions that must be checked in
order for the composition to be well defined are perhaps unintuitive. The
reasons why these conditions are necessary will become more apparent when
proving normal forms for QRE lenses.

@@

For example, recall that in the \bibtex{} to EndNote transformation, we had the
QREs \cd{bibtex} and \cd{endnote} and the bijective lens \cd{bib_to_end}
that maps between 
\cd{bibtex} and \cd{endnote}. The quotient lens that maps between
\cd{bibtex} and \cd{endnote} is then given by the following QRE lens:
